---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# evaluate.regressor

<!-- badges: start -->
<!-- badges: end -->

The goal of evaluate.regressor is to provide tools to evaluate supervised regressor outputs.

## Installation

You can install the development version of evaluate.regressor from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/evaluate.regressor")
```

## Example

This is a basic example which shows you how to evaluate a simple regressor:

```{r example}
library(evaluate.regressor)

# Evaluate a data.frame with at least two columns
my_pred <- data.frame(obs = sort(rnorm(n = 100)), 
                      pred = sort(rnorm(n = 100, mean = 0.6, sd = 1)))

# Evaluate using Spearman correlation 
base_metrics(my_pred, correlation = "spearman")

```

The function `base_metrics` calculates a given correlation score ('Spearman', 'Pearson' or 'Kendall'), root mean square error (RMSE), and R-squared.
